Exploring the Impact of Atypical Events on Regret: Analysis Through Hitchhiker, Car Accident, and Robbery Scenarios

### 2024-02-13 outputs/paper/paper.qmd
draft paper

The original paper used R [@citeR] for data processing and analysis in its replication package, we use R [@citeR]  as well for all data wrangling and analysis and R packages tidyverse [@tidy] to produce the figures.

>>>>

The original paper used R [@citeR] for data processing and analysis in its replication package, we use R [@citeR]  as well for all data wrangling and analysis and R packages tidyverse [@tidy],ggthemes[@ggthemes], patchwork[@patchwork], here[@here], ggplot2[@ggplot2], dplyr[@dplyr], psych[@psych],reshape2[@reshape2] to produce the figures.
